prolfqua (prodea) - An R-package for Proteomics Differential Expression Analysis.

### 2022-04-06 inst/MyArticle/paper.Rmd

```{r prolfquaModels}
xM <- data.frame( 
    lm = c("lm", "linear model on peptide or protein abundances", "strategy_lm, build_models, Contrasts"),
    lmer = c("lmer" , "mixed effect models on peptide and protein abundances", "strategy_lmer, build,models, Contrasts"),
    gmi = c("group mean imputation", "impute missing group means", "ContrastsSimpleImpute"),
    ROPECA = c("ROPECA","linear models on peptide abundances", "strategy_lm, build_models, Contrast, ContrastsROPECA"),
    limma = c("limma" , "empirical Bayes variance shrinkage", "ContrastsModerated"),
    pic = c("Protein interaction scoring", "by wrapping SAINT express binaries", "runSaint, ContrastsSaintExpress"),
    prodA = c("dropout model", "by warpping proDA functionality", "strategy_proDA, build_models, ContrastsProDa"), check.names =  FALSE)
xM <- data.frame(t(xM))
colnames(xM) <- c("m", "model", "prolfqua functions")
knitr::kable(xM[,2:3], caption = "Models available in prolfqua.",
             format = "latex", booktabs=TRUE) |>
    kableExtra::kable_styling(latex_options="scale_down")
```

>>>>

```{r prolfquaModels}
xM <- data.frame( 
    lm = c("lm", "linear model for peptides or proteins", "strategy_lm, Contrasts"),
    lmer = c("lmer" , "mixed effect models for peptides or proteins", "strategy_lmer, Contrasts"),
    gmi = c("group mean imputation", "impute missing group means", "ContrastsSimpleImpute"),
    ROPECA = c("ROPECA"," ", "ContrastsROPECA"),
    limma = c("limma" , "empirical Bayes variance shrinkage", "ContrastsModerated"),
    pic = c("SAINTexpress", "protein interaction scoring", "runSaint, ContrastsSaintExpress"),
    prodA = c("proDA", "dropout models", "strategy_proDA, Contrasts_proDa"), check.names =  FALSE)
xM <- data.frame(t(xM))

colnames(xM) <- c("id", "model", "prolfqua functions")
knitr::kable(tibble::as_tibble(xM[,1:3]), caption = "Models available in prolfqua.",
             format = "latex", booktabs=TRUE) |>
    kableExtra::kable_styling(latex_options="scale_down")
